\disstitle

### 2018-06-13 chapters/introduction/introduction.tex
many writings.

\brief{
The emerge of deep neural network brings light to the dream. The
neural network is a biological design, just like our brains. [history
of neural network]. Data and computational power bring us here.
}

In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.
%
Lee \etal~\cite{lee2017semantic} propose to detect semantic line
segments, which are able to segment the scene semantically, using
neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
\etal~\cite{yang2016object} explore to detect object contours with
CNNs.
%
Aside from edges and contours, another category of low-level
information that the CNNs can detect is the camera geometry, like
camera location, vanishing points, and horizon lines.
Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.

>>>>

During past dacades, many research has been done to detect the camera
geometry from input images. \todo{citation and examples}. Most of the
previous work optimize for a limited set of camera calibration
parameters only. However, our research found that there exists an
effective way of optimizing multiple camera calibration parameters at
simultaneously (refer to \chapref{mcmc}). Our method use the Monte
Carlo Markov Chain (MCMC) method to sample the possible solutions that
minimize the objective function, which measure the ``matchness''
between the observation (input image) and the camera calibration.

Among the most influential approaches for camera geometry estimation,
most methods are based on traditional statistics diagram. Not until a
fewer years ago, machine learning based methods gradually caught
people's attention in this area, thanks for the popularity of deep
neural network. Neural networks were first proposed in 80th
(\todo{citation}), The back-forward method develop by Hinton
\todo{citation} makes the effective training possible. However neural
networks are generally thought by researchers merely toy that can only
solve a very limited set of tasks. It is the develop of computational
resources and the big collection of annotated data that make the
neural networks deeper and eventually bring it to the stage of
industrial applications.

In the area of vanishing point detection, we are among the first
researches that use deep neural networks to solve the problem. The
deep neural networks prove to be a good tool to extract high-level
information that offer great help to conquer the problems in camera
geometry estimation. \todo{many citations}.
%
\newline \newline
%
In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.
%
Lee \etal~\cite{lee2017semantic} propose to detect semantic line
segments, which are able to segment the scene semantically, using
neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
\etal~\cite{yang2016object} explore to detect object contours with
CNNs.
%
Aside from edges and contours, another category of low-level
information that the CNNs can detect is the camera geometry, like
camera location, vanishing points, and horizon lines.
Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.
